Tweets

### 2020-05-15 Rmd/jse-2019-ms.Rmd
updated tweets analysis code

We used functions from the `rtweet` package to parse tweet JSON into a data frame. From there, we used `tidytext` R package functions to break the tweet text into individual words for latent Dirichlet allocation. We discarded commonly used "stop words" and emojis.

@@

@@

We sought to validate our hypothesis that we could detect a major social 
media event by examining tweet topic content at distinct time periods. 
As a proof of principle of our event detection strategy, we chose to 
analyze tweets before, during, and after the National Football League's 
2015 Super Bowl. We fitted latent Dirichlet allocation models for each of five 
distinct one-hour periods. The first period began approximately 48h 
before the Super Bowl halftime show. Subsequent time periods started at -24, 
0, +24, and +48 hours after the approximate start time of the halftime show. 
We defined each time period to be a single collection, or corpus, of tweets. Each tweet 
constituted a "document", in the terminology of text analysis. We then fitted latent 
Dirichlet allocation models to each corpus.

@@

We then inspected topic contents at each of the five time points.

>>>>

We used functions from the `rtweet` package to parse tweet JSON into a data frame. From there, we used `tidytext` R package 
functions to break the tweet text into individual words. We discarded commonly used "stop words" 
and emojis.

@@

### Latent Dirichlet allocation

Latent Dirichlet allocation is a statistical method for inferring latent (unobservable) topics (or themes)
from a collection (or corpus) of documents. It is a probabilistic, generative model 
for a corpus of documents. It is generative in the following sense. We pretend that
there's an imaginary process for creating documents in the corpus. For each document,
we choose a discrete distribution over topics. For example, some Mother's Day tweets wish 
mothers a happy celebration. This may constitute one topic in the corpus. 
Having chosen a distribution over topics, we then select document words by first 
drawing a topic from the distribution over topics, then drawing a word from the
chosen topic. 
Thus, a topic is technically defined as a distribution over words in a fixed vocabulary (or collection of words).

The literature on latent Dirichlet allocation and related methods is vast, 
and we won't attempt to review it here.

@@

We sought to validate our hypothesis that we could detect a major social 
media event by examining tweet topic content at distinct time periods. 
As a proof of principle of our event detection strategy, we chose to 
analyze tweets during and after Mother's Day 2020. We fitted latent Dirichlet allocation models for each of four 
distinct five-minute periods. The first period began at noon Eastern time on Mother's Day 2020. Subsequent time periods started 
24, 48, and 72 hours later. 
We defined each time period to be a single collection, or corpus, of tweets. We then fitted latent 
Dirichlet allocation models to each corpus.

@@

We then inspected topic contents at each of the four time points.

### 2020-05-15 Rmd/tweets.Rmd

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co"))
remove_reg <- "&amp;|&lt;|&gt;"
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

>>>>

```{r}
# create a twitter-specific stop word list
remove_reg <- "&amp;|&lt;|&gt;"
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co", "amp"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```
